\section{Survey Process}
\label{sec:process}

This survey focuses on dynamic binary translation and optimization. 
Before article collection stage, we designed several keywords such as "dynamic binary translation" and its abbreviation "DBT".
We also picked some strongly related keywords, such as "binary translation", "dynamic binary instrumentation", and "dynamic binary rewriting".
Based on these keywords, we conducted a comprehensive article collection on the top conferences and journals through AMiner, dblp, Google Scholar, and CNKI.

Table~\ref{tab:papers} shows the number of collected articles for each keyword when using the corresponding search tool.
In AMiner, we set the search options to conferences and journals in CCF A rank and CCF B rank.
These papers are most likely to be influential and are the articles of our follow-up focus.
In DBLP and CNKI, searching by keyword "DBT" will get a large number of irrelevant articles, so we ignore these results (marked as "/" in the table).
In Google Scholar, searching by keyword "DBT" gets 2780 results, which are difficult to check manually, so we discarded these results.

\begin{table}[!ht]
	\centering
	\caption{The number of collected papers under the given search tool and keyword before filtering.}
	\label{tab:papers}
	\scalebox{0.95}{
    \begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{Search tool} & \makecell{dynamic \\ binary \\ translation} & \makecell{DBT} & \makecell{binary translation} & \makecell{dynamic binary \\ instrumentation} & \makecell{dynamic binary \\ rewriting} \\ \hline
		AMiner          & 74    & 16                        & 113   & 8     & 6     \\ \hline
		DBLP            & 120   & /                         & 204   & 40    & 8     \\ \hline
		Google Scholar  & 261   & \textcolor{gray}{2780}    & 561   & 135   & 13    \\ \hline
		CNKI            & 98    & /                         & 187   & 5     & 2     \\ \hline
	\end{tabular}}
\end{table}

Then, we skimmed through the titles of these searched articles, filtering out articles that were apparently not relevant to DBT.
We also use some methods, such as sorting according to the number of citations, to collecte more influential articles.

Next, we snowballed through review articles retrieved in the previous stage.
We also selected some of the most cited papers to view related work.
Finally, we picked the most relevant and influential \textbf{114} articles on dynamic binary translation and optimizations.

In order to organize the collected articles, we build a mind map and classify these articles.
They are divided into four categories, including: 7 review articles, 63 optimization articles, 24 application articles, and 20 realted topic articles. 
Articles related to optimization are our focus and are further subdivided into five categories according to optimization methods, including: 7 memory optimization, 12 parallel optimization, 16 code layout optimization, 28 instruction level optimization, and 9 hardware-assisted optimization. 
